---
title: "biostatistics-assignment"
author: "Georgy Zaouk"
date: "2026-09-11"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Exercise 1

A study was conducted to investigate how effective a new diet was in lowering cholesterol. Results for the randomly selected subjects are shown below. The differences are assumed to have a normal distribution.

| Subject | A | B | C | D | E | F | G | H | I |
|--------:|---:|---:|---:|---:|---:|---:|---:|---:|---:|
| Before | 209 | 210 | 205 | 198 | 216 | 217 | 238 | 240 | 222 |
| After  | 199 | 207 | 189 | 209 | 217 | 202 | 211 | 223 | 201 |

Are the subjects' cholesterol levels lower on average after the diet?

Perform the appropriate test with $\alpha = 0.05$.

Find the appropriate confidence interval for the mean difference.

What do you conclude about this study?

```{r}

data_exo1 <- data.frame(
  Subject = c("A", "B", "C", "D", "E", "F", "G", "H", "I"),
  Before = c(209, 210, 205, 198, 216, 217, 238, 240, 222),
  After = c(199, 207, 189, 209, 217, 202, 211, 223, 201)
)

```

```{r}

t.test(data_exo1$Before, data_exo1$After, paired=TRUE)

```

# Exercise 2

A researcher measures how positive a person’s mood is and how creative he or she is,
obtaining the following interval scores :

| Creativity | Mood |
|-----------:|-----:|
| 7  | 10 |
| 6  | 8  |
| 11 | 9  |
| 4  | 6  |
| 5  | 5  |
| 7  | 3  |
| 4  | 7  |
| 5  | 2  |
| 6  | 4  |
| 4  | 1  |

I) Find the mean, median, mode, quartiles, 56th percentile, variance, standard deviation, minimum, and maximum of ‘creativity’.
Draw a histogram for ‘mood’.

II) You want to know if ‘creativity’ can be predicted from ‘mood’.

Prepare a scatter diagram in SPSS to study the relationship between ‘creativity’ and ‘mood’

Check the assumptions for the correlation test, perform then interpret it.

Use linear regression in SPSS to nd the 90 percent prediction interval for the slope.

Write the linear equation.

```{r}


```

